Publication wireframe

### 2020-05-25 vignette/191115_PMMB_DataWrangling_PM.Rmd
Chunk names Remove commented lines add missing AUDPC scoring in king11

#### AUDPC curve
```{r}
library(ggplot2)

@@

#### Input trial data  
```{r Herm11_dataInput}
Herm_11_dat <- 
   data.frame(trial_ref = "mung1011/01",
              year = "2011",
              location = "Hermitage",
              host_genotype = Herm_11$`Cultivar!`,
              trial_design = "RCB",
              plot_length = 11,
              plot_width = 4,
              plant_density = NA,
              row_spacing = 0.75,
              replicate = Herm_11$`Rep!`,
              planting_date = as.Date("2011-01-24", format = "%Y-%m-%d"),
              emergence_date = NA,
              flowering_date = as.Date("2011-03-22", format = "%Y-%m-%d"),
              pod_fill_date = NA,
              mid_late_pod_fill = NA,
              first_sign_disease = as.Date("2011-03-28", format = "%Y-%m-%d"),
              trade_name = as.factor(Herm_11$trade_name),
              fungicide_ai = Herm_11$fungicide_ai,
              dose_ai.ha = Herm_11$dose_ai.ha,
              n_treatment = Herm_11$Tr,
              fungicide_application_1 = Herm_11$fungicide_application_1,
              fungicide_application_2 = Herm_11$fungicide_application_2,
              fungicide_application_3 = Herm_11$fungicide_application_3,
              total_fungicide = Herm_11$total_fungicide,
              harvest_date = as.Date("2011-04-25", format = "%Y-%m-%d"),
              final_assessment = as.Date("2011-04-11", format = "%Y-%m-%d"),
              PM_final_severity = Herm_11$`P.M. 11  w.a.p.`,
              # AUDPC = apply(data.frame(zero = rep(0,42),
              #                          wap11 = Herm_11[,c("P.M. 11  w.a.p.")]-1),1, 
              #               FUN = audpc, dates = c((as.Date("2011-03-28", format = "%Y-%m-%d")-7)- # First sign of disease minus planting date. Gives when there is no disease
              #                                         as.Date("2011-01-24", format = "%Y-%m-%d"),
              #                  77)), # -1 to the data because zero disease = 1 on rating scale
              rating_scale = "1-9",
              grain_yield.t.ha. = Herm_11$`Yld Kg/ha`,
              stringsAsFactors = FALSE)

@@

#### AUDPC curve
```{r}

@@

King_11_dat <- cbind(King_11_dat,
                     AUDPC = apply(data.frame(zero = 0,
                                              King_11[,c("9 w.a.p.","11 w.a.p.","14 w.a.p.")]-1),
                                   1, 
                                   FUN = audpc,
                                   dates = c((King_11_dat$first_sign_disease[1]-7)-
                                                King_11_dat$planting_date[1],
                                             9*7,11*7,14*7)
                                   ),
                     AUDPS = apply(data.frame(zero = 0,
                                                   King_11[,c("9 w.a.p.","11 w.a.p.","14 w.a.p.")]-1),
                                        1, 
                                        FUN = audps, 
                                        dates = c((King_11_dat$first_sign_disease[1]-7)-
                                                     King_11_dat$planting_date[1],
                                                  9*7,11*7,14*7)
                                        )
                          )

King_11$PM_zero <- 1
King11_plot <- melt(King_11, id.vars = c("Treatment!","cultivar","rep!","spray_n","fungicide"),
                  measure.vars = c("PM_zero","9 w.a.p.","11 w.a.p.","14 w.a.p."))

King11_plot <- King11_plot %>%
   mutate(T_var = case_when(variable == "PM_zero" ~ 
                               as.numeric((King_11_dat$first_sign_disease[1]-7) - King_11_dat$planting_date[1]),
                            variable == "9 w.a.p." ~ 9*7,
                            variable == "11 w.a.p." ~ 11*7,
                            variable == "14 w.a.p." ~ 14 *7)
   )

>>>>

#### AUDPC curve
```{r Herm10_audpc}
library(ggplot2)

@@

#### Input trial data  
```{r Herm11_dataInput}
Herm_11_dat <- 
   data.frame(trial_ref = "mung1011/01",
              year = "2011",
              location = "Hermitage",
              host_genotype = Herm_11$`Cultivar!`,
              trial_design = "RCB",
              plot_length = 11,
              plot_width = 4,
              plant_density = NA,
              row_spacing = 0.75,
              replicate = Herm_11$`Rep!`,
              planting_date = as.Date("2011-01-24", format = "%Y-%m-%d"),
              emergence_date = NA,
              flowering_date = as.Date("2011-03-22", format = "%Y-%m-%d"),
              pod_fill_date = NA,
              mid_late_pod_fill = NA,
              first_sign_disease = as.Date("2011-03-28", format = "%Y-%m-%d"),
              trade_name = as.factor(Herm_11$trade_name),
              fungicide_ai = Herm_11$fungicide_ai,
              dose_ai.ha = Herm_11$dose_ai.ha,
              n_treatment = Herm_11$Tr,
              fungicide_application_1 = Herm_11$fungicide_application_1,
              fungicide_application_2 = Herm_11$fungicide_application_2,
              fungicide_application_3 = Herm_11$fungicide_application_3,
              total_fungicide = Herm_11$total_fungicide,
              harvest_date = as.Date("2011-04-25", format = "%Y-%m-%d"),
              final_assessment = as.Date("2011-04-11", format = "%Y-%m-%d"),
              PM_final_severity = Herm_11$`P.M. 11  w.a.p.`,
              rating_scale = "1-9",
              grain_yield.t.ha. = Herm_11$`Yld Kg/ha`,
              stringsAsFactors = FALSE)

@@

#### AUDPC curve
```{r Herm_audpc}

@@

King_11_dat <- cbind(King_11_dat,
                     AUDPC = apply(data.frame(zero = 0,
                                              King_11[,c("9 w.a.p.","11 w.a.p.","12 w.a.p.","14 w.a.p.")]-1),
                                   1, 
                                   FUN = audpc,
                                   dates = c((King_11_dat$first_sign_disease[1]-7)-
                                                King_11_dat$planting_date[1],
                                             9*7,11*7,12*7,14*7)
                                   ),
                     AUDPS = apply(data.frame(zero = 0,
                                                   King_11[,c("9 w.a.p.","11 w.a.p.","12 w.a.p.","14 w.a.p.")]-1),
                                        1, 
                                        FUN = audps, 
                                        dates = c((King_11_dat$first_sign_disease[1]-7)-
                                                     King_11_dat$planting_date[1],
                                                  9*7,11*7,12*7,14*7)
                                        )
                          )

King_11$PM_zero <- 1
King11_plot <- reshape2::melt(King_11, id.vars = c("Treatment!","cultivar","rep!","spray_n","fungicide"),
                  measure.vars = c("PM_zero","9 w.a.p.","11 w.a.p.","12 w.a.p.","14 w.a.p."))

King11_plot <- King11_plot %>%
   mutate(T_var = case_when(variable == "PM_zero" ~ 
                               as.numeric((King_11_dat$first_sign_disease[1]-7) - King_11_dat$planting_date[1]),
                            variable == "9 w.a.p." ~ 9*7,
                            variable == "11 w.a.p." ~ 11*7,
                            variable == "12 w.a.p." ~ 12*7,
                            variable == "14 w.a.p." ~ 14 *7)
   )
